Here is the LaTeX code to reproduce the **RV College of Engineering Invention Disclosure Form**. I have formatted it using the `article` class with adjustments to margins and spacing to mimic a professional form layout. The instructions provided in the source text (inside the `< >` brackets) are italicized to distinguish them from the field headers.

```latex
\documentclass[a4paper,12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{titlesec}

% Adjust section formatting to look more like form headers
\titleformat{\section}
  {\normalfont\large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{0.5ex plus .2ex}

\begin{document}

% --- Header ---
\begin{center}
    \textbf{\Large RV College of Engineering} \\
    Bangalore \\
    \textbf{IP Cell} \\
    \vspace{0.5cm}
    \textbf{\Large Invention Disclosure Form (IDF)}
\end{center}

\vspace{0.5cm}

% --- Reference Information ---
\noindent \textbf{Invention No:} RVCE-Dept Name-Inventor Initial- 3 digit no (starting from 001) \hfill \textbf{Version:} 00

\hrulefill

% --- Main Form Fields ---

\section*{Title of the invention}
\vspace{1cm} % Space for user input

\section*{Name, designation, Department, email id and phone no: of the inventors (In order of primary contact and so)}
\vspace{1cm}

\section*{Residential address of all the inventors}
\vspace{1cm}

\section*{Brief Description - Describe the invention - What does it do? How does it do it?}
\vspace{2cm}

\section*{Details of the Invention}
\textit{<In this section, explain the following:
\begin{itemize}[noitemsep]
    \item Modules, steps, parts that make up the invention, in its best form
    \item What does each contribute to the invention?
    \item Which are new to this invention?
    \item In what way do they interact to make the invention work?
    \item To make it better, use labeled figures, flow charts, pictures to detail your invention
    \item Exact measurements are not required, unless they are essential to the working of the invention>
\end{itemize}}
\vspace{3cm}

\section*{Please briefly describe the problem that the technology solves and its advantages/benefits relative to competing technologies or products.}
\vspace{2cm}

\section*{What product might this invention become?}
\vspace{1cm}

\section*{Alternatives and limitations of the proposed invention}
\vspace{1cm}

\section*{Current state of art}
\textit{<In this section, explain the following:
\begin{itemize}[noitemsep]
    \item How is the proposed solution to a problem of the invention being done today?
    \item What is the nearest method or system you are aware of to your invention?
    \item Is there something available, which performs the same in a different way?
    \item Is there any combination of existing methods which would be similar to your invention?
    \item How does your invention perform different or better than the existing methods?
    \item List references (patent or non-patent) related to your work>
\end{itemize}}
\vspace{3cm}

\section*{Public Disclosures:}
\begin{enumerate}
    \item Is this invention or work is published in any journal, conference, seminar, workshop or any public meeting?
    \item Is this work or invention is sent to any competition?
    \item Is this work is presented to customers?
    \item Is this work is submitted to any funding agencies?
\end{enumerate}
\vspace{1cm}

\section*{Commercial Potential}
\textbf{Mention possible products, solution, services that can be made from this inventions}
\vspace{1cm}

\textbf{Mention the companies or industries that are most likely to be interested in this technology}
\vspace{1cm}

\textbf{Mention which of the following best describes your invention disclosure:}
\begin{itemize}[noitemsep]
    \item [$\square$] Has significant commercial value
    \item [$\square$] Is a method or platform or technology that can go to existing product, solution or services
    \item [$\square$] Particular company may be interested in this invention
    \item [$\square$] I/we can start a start-up company using this invention
\end{itemize}

\end{document}

```